Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

 While the introduction of new medical measurement methods requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally important for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality.

>>>>

 While the introduction of new medical measurement methods requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally important for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality. Conventionally, the methods are evaluated using distance measures that take aggregated local absolute differences between predictions (or measurements) and target values into account. For example, the Continuous Ranked Probability Score (CRPS) can be used to evaluate the accuracy of probabilistic predictions. It is also based on the integrated squared differences between the cumulative distribution function (CDF) of the prediction and the Heaviside jump function. These measures all fail to take sufficient account of whether the right direction of change is being taken, which can often be highly relevant in practice.
